Particle Swarm Optimization for Crystallography

### 2009-01-06 crystallography/paper.tex
Some initial work on an intro

\title{MRPSO: MapReduce Particle Swarm Optimization}
\numberofauthors{4}
%\author{%
%\alignauthor Matthew Gardner\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{mjg82@cs.byu.edu}
%\alignauthor Andrew McNabb\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{a@cs.byu.edu}
%\alignauthor Branton Campbell\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Physics Dept.}\\
%    \affaddr{N261 ESC, Provo, UT 84602}\\
%    \email{branton_campbell@byu.edu}
%\alignauthor Kevin Seppi\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{k@cs.byu.edu}
%}
\date{}

@@

@@

TODO.

>>>>

\title{Particle Swarm Optimization for Crystallography}
\numberofauthors{4}
%\author{%
%\alignauthor Matthew Gardner\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{mjg82@cs.byu.edu}
%\alignauthor Andrew McNabb\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{a@cs.byu.edu}
%\alignauthor Branton Campbell\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Physics Dept.}\\
%    \affaddr{N261 ESC, Provo, UT 84602}\\
%    \email{branton_campbell@byu.edu}
%\alignauthor Kevin Seppi\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{k@cs.byu.edu}
%}
\date{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction

@@

TODO.
Particle swarm optimization is most often used with functions that are quickly
evaluated.  Many real-life problems take much longer.  What does one do when 
presented with a function that takes several minutes or hours to evaluate?

In this paper we present a crystallography problem whose function evaluation
takes several minutes to evaluate.  We discuss issues in solving this problem
specifically, and in optimizing expensive functions in general with particle 
swarm optimization.
